|

### 2019-07-15 appendix/appendix-institutional-design-climate-policy.Rmd
revisions v1.0

---
title: |
       | Supplementary Materials for "Do Elites Support Polycentric Climate Governance? Evidence from Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: "16 May 2019"
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
header-includes:
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
---

@@

[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, [davidskarbek@brown.edu](mailto:david_skarbek@brown.edu), <http://davidskarbek.com>.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('freire-mignozzetti-skarbek.RData')

@@

From 1st of October to 5th of December 2018, we run an elite survey in ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru. The survey proceeded in two steps.

@@

In our research, we ask what features elite members would like to see implemented in a climate change agreement. We ask their opinion on 6 questions: 1) who makes the rules; 2) who enforces the laws; 3) what punishment should be used against lawbreakers; 4) how are repeated violations punished; 5) how are costs distributed, and 6) how often the agreement will be renegotiated. Each of the questions has four to five different attributes. For the first two questions, we ask individuals if they would rather have the community, local governments, federal governments, or international organisations to create or enforce rules. As for punishments, we have options ranging from do nothing to fines and incarceration. We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluter countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation. Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, what we see as a proxy for the stability of rules. Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient. 
Conjoint experiments have many advantages. First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs. The design thus maximises our research budget. Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments. In that regard, our conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration. Finally, as the experiments consist of a simple choice between A and B, conjoint analyses are easy to understand and to implement. This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.

@@

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5}
aux <- cj %>%
  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
  unique()

@@

# Frequency of features selected by each attribute

@@

```{r codefig2}
## Main plot

# Main estimation equation
fm <- selected ~ `Who makes the rules?` +
  `How are conflicts resolved?` +
  `What punishments do they use?` + 
  `How are repeated violations punished?` +
  `How are costs distributed?` +
  `How often will the agreement be renegotiated?`

# Plot
mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0=0.5)
p <- plot_mm(mms, vline = 0.5)
ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)
p

@@

# Argentina
arg <- mm(subset(cj, countryOrigin=='Argentina'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(arg, capt = 'Marginal Means -- Argentina Only')
```

@@

```{r}
# Bolivia
bol <- mm(subset(cj, countryOrigin=='Bolivia'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
```

@@

```{r}
# Brazil
bra <- mm(subset(cj, countryOrigin=='Brazil'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(bra, capt = 'Marginal Means -- Brazil Only')
```

@@

```{r}
# Chile
chi <- mm(subset(cj, countryOrigin=='Chile'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(chi, capt = 'Marginal Means -- Chile Only')
```

@@

```{r}
# Colombia
col <- mm(subset(cj, countryOrigin=='Colombia'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(col, capt = 'Marginal Means -- Colombia Only')
```

@@

```{r}
# Costa Rica
cri <- mm(subset(cj, countryOrigin=='Costa Rica'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
```

@@

```{r}
# Ecuador
ecu <- mm(subset(cj, countryOrigin=='Ecuador'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
```

@@

```{r}
# Mexico
mex <- mm(subset(cj, countryOrigin=='Mexico'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(mex, capt = 'Marginal Means -- Mexico Only')
```

@@

```{r}
# Panama
pan <- mm(subset(cj, countryOrigin=='Panama'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(pan, capt = 'Marginal Means -- Panama Only')
```

@@

```{r}
# Peru
per <- mm(subset(cj, countryOrigin=='Peru'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(per, capt = 'Marginal Means -- Peru Only')
```

@@

```{r, fig.width = 10, fig.height = 10}
# Changing country labels
arg$country <- 'Argentina'
bol$country <- 'Bolivia'
bra$country <- 'Brazil'
chi$country <- 'Chile'
col$country <- 'Colombia'
cri$country <- 'Costa Rica'
ecu$country <- 'Ecuador'
mex$country <- 'Mexico'
pan$country <- 'Panama'
per$country <- 'Peru'
# Plot by country
p <- plot_mm(rbind(arg, bol, bra, chi, col, 
              cri, ecu, mex, pan, per), 
        group = 'country', vline = 0.5, nr=10) +
  facet_wrap( ~ country, ncol=5)
ggsave(filename = 'MM_country.pdf', 
       plot = p, width = 12, height = 12)
p
```

@@

# Table for the Executive
res1 <- mm(subset(cj, groupOrigin=='Executive'), 
           fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res1, capt = 'Marginal Means -- Executive Only')
```

@@

```{r}
# Legislative
res2 <- mm(subset(cj, groupOrigin=='Legislative'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res2, capt = 'Marginal Means -- Legislative Only')
```

@@

```{r}
# Civil Society
res3 <- mm(subset(cj, groupOrigin=='Civil Society'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
```

@@

```{r}
# Academia
res4 <- mm(subset(cj, groupOrigin=='Academia'), 
        fm, id = ~Response.ID, alpha = .1, h0=0.5)
table_mm(res4, capt = 'Marginal Means -- Academia Only')

@@

# Plot by Elite Type
p <- plot_mm(rbind(res1, res2, res3, res4), 
     group = 'MemberType', vline = 0.5, nr=4) + 
  facet_wrap( ~ MemberType, ncol=4)
p
ggsave(filename = 'MM_membertype.pdf', plot = p, 
       width = 8, height = 5)
```

@@

```{r}
## Main model
rm(cj)
load('freire-mignozzetti-skarbek.RData')
# Set conjoint baselines
baselines <- list()
baselines$`How often will the agreement be renegotiated?` <- "One year"
baselines$`What punishments do they use?` <- 'None'
baselines$`How are conflicts resolved?` <- 'Government bureaucracy'
baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
attrs <- 
  c("How are conflicts resolved?",
    "How are costs distributed?",
    "How are repeated violations punished?",
    "How often will the agreement be renegotiated?",
    "What punishments do they use?",
    "Who makes the rules?"
    )

results <- 
  cjoint::amce(fm, data=cj, cluster=T, 
               respondent.id="Response.ID", 
               design=conjDesign, 
               baselines = baselines, na.ignore = T)
```

@@

```{r}
# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Full Model')
```

```{r, fig.width = 7, fig.height = 8}
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs)
```

>>>>

---
title: |
       | Supplementary Materials for "Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
header-includes:
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
---

@@

[^skarbek]: The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, <davidskarbek@brown.edu>, <http://davidskarbek.com>.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('/Users/politicaltheory/Documents/github/climate/appendix/freire-mignozzetti-skarbek.RData')

@@

\setlength{\parindent}{1cm}
\setlength{\parskip}{0pt}

From 1st of October to 5th of December 2018, we run an elite survey with respondents from ten Latin American countries: Argentina, Bolivia, Brazil, Chile, Colombia, Costa Rica, Ecuador, Mexico, Panama, and Peru. The survey proceeded in two steps.

@@

In our research, we ask what features elite members would like to see implemented in a climate change agreement. We ask their opinion on 6 questions: 1) who makes the rules; 2) who enforces the laws; 3) what punishment should be used against lawbreakers; 4) how are repeated violations punished; 5) how are costs distributed, and 6) how often the agreement will be renegotiated. Each of the questions has four to five different attributes. For the first two questions, we ask individuals if they would rather have the community, local governments, federal governments, or international organisations to create or enforce rules. As for punishments, we have options ranging from do nothing to fines and incarceration. We ask whether the costs of climate change agreements should be paid mostly or exclusively by developed countries, by polluter countries regardless of their wealth, or if costs should be allocated according to the history of emissions of a given nation. Individuals also state their preferences for short-term agreements, a proxy we use for flexibility, or for long-term ones, what we see as a proxy for the stability of rules. Lastly, we ask which of the two conjoined choices individuals perceive as more legitimate and more efficient.

Conjoint experiments have many advantages. First, as each individual chooses between many pairs of possible climate agreements -- seven in our case -- we can drastically increase our sample size without incurring in further financial costs. The design thus maximises our research budget. Second, individuals rarely decide considering one attribute at a time, as presented in other types of survey experiments. In that regard, our conjoint analysis mirrors how people naturally make their choices, that is, by simultaneously taking several characteristics into consideration. Finally, as the experiments consist of a simple choice between A and B, conjoint analyses are easy to understand and to implement. This research design reduces the cognitive load interviewees have while answering surveys and as a result, we can expect more accurate responses from our sample.

@@

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
aux <- cj %>%
  select(Response.ID, countryOrigin, groupOrigin, LocationLongitude, LocationLatitude) %>%
  unique()

@@

# Frequency of Features Selected by Each Attribute

@@

```{r codefig2}
## Main plot
# Main estimation equation
fm <- selected ~ `Who makes the rules?` +
  `How are conflicts resolved?` +
  `What punishments do they use?` + 
  `How are repeated violations punished?` +
  `How are costs distributed?` +
  `How often will the agreement be renegotiated?`

# Plot
mms <- mm(cj, fm, id = ~Response.ID, alpha = .1, h0=0.5)
p <- plot(mms, vline = 0.5)
p
ggsave(filename = 'MM_all.pdf', plot = p, width = 6, height = 5)

@@

# Argentina
arg <- mm(subset(cj, countryOrigin=='Argentina'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(arg, capt = 'Marginal Means -- Argentina Only')
```

@@

```{r}
# Bolivia
bol <- mm(subset(cj, countryOrigin=='Bolivia'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(bol, capt = 'Marginal Means -- Bolivia Only')
```

@@

```{r}
# Brazil
bra <- mm(subset(cj, countryOrigin=='Brazil'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(bra, capt = 'Marginal Means -- Brazil Only')
```

@@

```{r}
# Chile
chi <- mm(subset(cj, countryOrigin=='Chile'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(chi, capt = 'Marginal Means -- Chile Only')
```

@@

```{r}
# Colombia
col <- mm(subset(cj, countryOrigin=='Colombia'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(col, capt = 'Marginal Means -- Colombia Only')
```

@@

```{r}
# Costa Rica
cri <- mm(subset(cj, countryOrigin=='Costa Rica'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(cri, capt = 'Marginal Means -- Costa Rica Only')
```

@@

```{r}
# Ecuador
ecu <- mm(subset(cj, countryOrigin=='Ecuador'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(ecu, capt = 'Marginal Means -- Ecuador Only')
```

@@

```{r}
# Mexico
mex <- mm(subset(cj, countryOrigin=='Mexico'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(mex, capt = 'Marginal Means -- Mexico Only')
```

@@

```{r}
# Panama
pan <- mm(subset(cj, countryOrigin=='Panama'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(pan, capt = 'Marginal Means -- Panama Only')
```

@@

```{r}
# Peru
per <- mm(subset(cj, countryOrigin=='Peru'),  
        fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(per, capt = 'Marginal Means -- Peru Only')
```

@@

```{r, fig.width = 10, fig.height = 10}
# Changing country labels
arg$country <- 'Argentina'
bol$country <- 'Bolivia'
bra$country <- 'Brazil'
chi$country <- 'Chile'
col$country <- 'Colombia'
cri$country <- 'Costa Rica'
ecu$country <- 'Ecuador'
mex$country <- 'Mexico'
pan$country <- 'Panama'
per$country <- 'Peru'
# Plot by country
p <- plot(rbind(arg, bol, bra, chi, col, 
              cri, ecu, mex, pan, per), 
        group = 'country', vline = 0.5, nr = 10) +
  facet_wrap( ~ country, ncol = 5)

p

ggsave(filename = 'MM_country.pdf', 
       plot = p, width = 12, height = 12)
```

@@

# Table for the Executive
res1 <- mm(subset(cj, groupOrigin=='Executive'), 
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res1, capt = 'Marginal Means -- Executive Only')
```

@@

```{r}
# Legislative
res2 <- mm(subset(cj, groupOrigin=='Legislative'), 
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res2, capt = 'Marginal Means -- Legislative Only')
```

@@

```{r}
# Civil Society
res3 <- mm(subset(cj, groupOrigin=='Civil Society'), 
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res3, capt = 'Marginal Means -- Civil Society Only')
```

@@

```{r}
# Academia
res4 <- mm(subset(cj, groupOrigin=='Academia'), 
           fm, id = ~Response.ID, alpha = 0.1, h0 = 0.5)
table_mm(res4, capt = 'Marginal Means -- Academia Only')

@@

# Plot by Elite Type
p <- plot(rbind(res1, res2, res3, res4), 
     group = 'MemberType', vline = 0.5, nr=4) + 
  facet_wrap( ~ MemberType, ncol=4)
p

ggsave(filename = 'MM_membertype.pdf', plot = p, 
       width = 8, height = 5)
```

@@

```{r, fig.width = 7, fig.height = 8}
## Main model
rm(cj)
load('freire-mignozzetti-skarbek.RData')

# Set conjoint baselines
baselines <- list()
baselines$`How often will the agreement be renegotiated?` <- "One year"
baselines$`What punishments do they use?` <- 'None'
baselines$`How are conflicts resolved?` <- 'Government bureaucracy'
baselines$`How are costs distributed?` <- 'Rich countries pay more than poor countries'
baselines$`Who makes the rules?` <- 'Federal government'

attrs <- 
  c("Who makes the rules?",
    "How are conflicts resolved?",
    "What punishments do they use?",
    "How are repeated violations punished?",
    "How are costs distributed?",
    "How often will the agreement be renegotiated?")

results <- 
  cjoint::amce(fm, data=cj, cluster=T, 
               respondent.id="Response.ID", 
               design=conjDesign, 
               baselines = baselines, na.ignore = T)

# Table AMCE -- Full Model 
tableAMCE(results, capt = 'AMCE -- Full Model')
```

@@

```{r, fig.width = 7, fig.height = 8}
# Plot AMCE -- Full Model
plot(results, ci=0.9, point.size = .8, dodge.size = 1,
     text.size = 10, main = 'AMCE -- Full Model',
     attribute.names = attrs)
```
